### 2021-01-18 papers/jin-thesis/Chapters/4Results.tex
Added a lot to my thesis directory
Worked on thesis

\section{Optimized Parameters}
\textit{Talk about best-fit parameters that matched experimentalists data. Include table with all parameters.}
\section{Stepping Patterns}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle. Displacement is defined as the unbounded binding domain x position minus the binded binding domain x position, calculated before and after a step. Linear regression of the probability distribution indicates a dependence the final displacement of the step and its initial displacement, similarly to experiment. \textit{Bottom:} One dimensional probability density of step length. Step length defined as final displacement minus the initial displacement. Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.} 
	\label{fig:final_disp}
\end{figure}

>>>>

\section{Optimized Parameters}
\textit{Talk about best-fit parameters that matched experimentalists data. Include table with all parameters.}

%\section{Stepping Patterns}
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
%	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
%	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle. Displacement is defined as the unbounded binding domain x position minus the binded binding domain x position, calculated before and after a step. Linear regression of the probability distribution indicates a dependence the final displacement of the step and its initial displacement, similarly to experiment. \textit{Bottom:} One dimensional probability density of step length. Step length defined as final displacement minus the initial displacement. Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.} 
%	\label{fig:final_disp}
%\end{figure}
